TODO: A Survey of StarCraft AI Techniques

### 2013-02-20 survey.tex
Updated game state sizes with DAve's information

\begin{itemize}
\item They are {\em simultaneous move} games, where more than one player can issue actions at the same time. Additionally, these actions are {\em durative}, i.e. actions are not instantaneous, but take some amount of time time to complete.
\item RTS games are ``real-time'', which actually means is that each player has a very small amount of time to decide the next move. Compared to Chess, where players have several minutes to decide the next action, in Starcraft, the game executes at 24 iterations per second, which means that players only have 55ms to decide a move, before the game state changes.
\item Most RTS games are partially observable: players can only see the part of the map that has been explored.
\item Most RTS games are non-deterministic.
\item And finally, the complexity of these games, both in terms of state space size and in terms of number of actions available at each decision cycle is very large. {\color{red} For example, the state space of Chess is typically estimated to be around $10^{50}$, whereas the state space of Starcraft in a typical map is estimated to be around $10^{10000}$.}
\end{itemize}

>>>>

\begin{itemize}
\item They are {\em simultaneous move} games, where more than one player can issue actions at the same time. Additionally, these actions are {\em durative}, i.e. actions are not instantaneous, but take some amount of time time to complete.
\item RTS games are ``real-time'', which actually means is that each player has a very small amount of time to decide the next move. Compared to Chess, where players have several minutes to decide the next action, in Starcraft, the game executes at 24 iterations per second, which means that players only have 55ms to decide a move, before the game state changes.
\item Most RTS games are partially observable: players can only see the part of the map that has been explored.
\item Most RTS games are non-deterministic.
\item And finally, the complexity of these games, both in terms of state space size and in terms of number of actions available at each decision cycle is very large. For example, the state space of Chess is typically estimated to be around $10^{50}$, heads up no-limit texas holdem poker around $10^{80}$, and Go around $10^{170}$. In comparison, the state space of Starcraft in a typical map is estimated to be at least {\color{red} $10^{10000}$.}
\end{itemize}
